\textit{Supplementary materials for}: Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-02-25 paper/supplement.tex
fixed supplementary figure names and references in main text
new topic-word distributions supp fig & caption

\renewcommand{\figurename}{Supplementary Figure}

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

@@

@@

\caption{\textbf{Topic weights. A. Average topic weights for each lecture and
question set}. The bar plots display each topic's average weight across
lecture timepoints (top row) and questions (bottom row); colors denote topics.
The top-weighted words from the highest-weighted topic from each lecture are
displayed in the upper right (orange: topic 2; yellow-green: topic 4). The
top-weighted words from the full set of topics may be found in
Table~\ref{tab:topics}. \textbf{B. Relationships between average topic
weights.} Pairwise correlations between the distributions of average topic
weights for each lecture and question set. Each row and column corresponds
to a bar plot in Panel A. Also see Figure~\topics~in the main text.}

>>>>

\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplementary Table}

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
%\renewcommand{\theequation}{S\arabic{equation}}
%\renewcommand{\thefigure}{S\arabic{figure}}
%\renewcommand{\thetable}{S\arabic{table}}
%\renewcommand{\bibnumfmt}[1]{[S#1]}
%\renewcommand{\citenumfont}[1]{S#1}

@@

\begin{figure}[tp]
    \includegraphics[width=\textwidth]{figs/topic-word-distributions}

    \caption{\textbf{Topic-word distributions}. Each topic is defined by a distribution 
    of weights over words in the topic model's vocabulary (i.e., the union of all unique 
    words from the two lectures' transcripts, excluding stop-words, after 
    preprocessing). Each plot above displays the weights for the (up to) 50 words 
    weighted most heavily by an individual topic extracted from the lectures' contents (see 
    \textit{Constructing text embeddings of multiple lectures and questions}).}

    \label{fig:topic-word-distributions}
\end{figure}

@@

\caption{\textbf{Topic weights. A. Average topic weights for each lecture and
question set}. The bar plots display each topic's average weight across
lecture timepoints (top row) and questions (bottom row); colors denote topics.
The top-weighted words from the highest-weighted topic from each lecture are
displayed in the upper right (orange: topic 2; yellow-green: topic 4). The
top-weighted words from the full set of topics may be found in Supplementary
Table~\ref{tab:topics}. \textbf{B. Relationships between average topic
weights.} Pairwise correlations between the distributions of average topic
weights for each lecture and question set. Each row and column corresponds
to a bar plot in Panel A. Also see Figure~\topics~in the main text.}
